
\documentclass[a4paper,10pt]{article}

\usepackage[margin=1.2cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage{array}

% Formatting tweaks
\pagenumbering{gobble} % remove page numbers
\setlength{\parskip}{3pt}
\setlist[itemize]{topsep=2pt,itemsep=2pt,parsep=0pt,leftmargin=12pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]

\begin{document}

%====================
% HEADER
%====================
{\LARGE \textbf{Protick Roy}}\\[-1pt]
Dhaka, Bangladesh \textbar{} Remote \\[-1pt]
\href{mailto:protickrr@gmail.com}{protickrr@gmail.com} \textbar{} +8801301212424 \textbar{} 
\href{https://www.linkedin.com/in/protickroy}{linkedin.com/in/protickroy} \textbar{} 
\href{https://github.com/protickr}{github.com/protickr}

\vspace{6pt}

%====================
% EXPERIENCE
%====================
\section*{Experience}

\textbf{Software Engineer} \hfill Aug 2023 -- Present\\[-2pt]
\textit{Ngaze Inc. \textbar{} Dhaka, Bangladesh \textbar{} Remote}\\[-4pt]
\begin{itemize}
  \item Developed and maintained RESTful backend APIs, improving data handling efficiency and reducing average response time by 30\%.
  \item Deployed and monitored production workloads on GCP using Docker and Kubernetes, achieving 99.9\% uptime.
  \item Resolved high-priority frontend bugs and delivered new UI features using JavaScript and React.
  \item Led feature planning and end-to-end development in alignment with client and stakeholder requirements.
\end{itemize}

\textbf{Freelance Software Engineer} \hfill Oct 2020 -- Aug 2023\\[-2pt]
\textit{Independent contractor under a small collective (MAPSIT umbrella)}\\[-4pt]
\begin{itemize}
  \item \textbf{Dollabills} (\href{https://dollabills.club}{dollabills.club}) --- Social platform with real-time chat and video conferencing; built core features and deployed on AWS EC2. \emph{PHP, Laravel, JavaScript, AWS Chime, WebRTC, WebSocket}
  \item \textbf{CPRExchange} (\href{https://cprexchange.com}{cprexchange.com}) --- Recommerce marketplace delivering listing workflows and secure payments on DigitalOcean. \emph{PHP, Laravel}
  \item \textbf{Inventory \& HR Management System} (\href{http://shabinkhan.com}{shabinkhan.com}, offline) --- Inventory, HR, role-based auth; deployed on DigitalOcean VPS. \emph{TypeScript, JavaScript, Express.js, TypeORM, Next.js, MySQL}
\end{itemize}

\textbf{Junior Software Engineer} \hfill Sep 2019 -- Apr 2020\\[-2pt]
\textit{Divine IT Limited}\\[-4pt]
\begin{itemize}
  \item Built a Django web app to manage attendance devices, process records, and sync with ERP via REST APIs.
  \item Implemented real-time device monitoring, cutting downtime detection time by 40\%.
  \item Fixed ERP bugs and shipped features that improved system stability.
\end{itemize}

\textbf{Junior Full Stack Web Application Developer} \hfill Oct 2018 -- Jul 2019\\[-2pt]
\textit{BFIN IT Limited}\\[-4pt]
\begin{itemize}
  \item Delivered ERP features and maintenance using HTML, CSS, JavaScript, and PHP.
  \item Improved UI responsiveness and cross-browser compatibility, reducing reported UI issues by 25\%.
\end{itemize}

%====================
% PROJECTS
%====================
\section*{Projects}
\begin{itemize}
  \item \textbf{The Wild Oasis} (\href{https://oasisprotick.vercel.app/login}{oasisprotick.vercel.app/login}) --- Hotel management app with secure auth, booking flows, and admin dashboard; state managed with Redux and deployed on Vercel. \emph{React, Redux, styled-components, Vite, Vercel}
  \item \textbf{Video Surveillance \& Security System} (\href{https://github.com/protickr/video_surveillance_and_security_system}{github.com/protickr/video\_surveillance\_and\_security\_system}) --- IoT security system using computer vision to detect motion in real time and email snapshot alerts; includes Raspberry Pi setup steps. \emph{Python, OpenCV, Raspberry Pi, Shell, PHP, JavaScript}
  \item \textbf{Food Recipe App} (\href{https://forkify-protickrr.netlify.app}{forkify-protickrr.netlify.app}) --- Responsive recipe app with bookmarking, editing, and CRUD operations. \emph{JavaScript, SASS}
\end{itemize}

%====================
% SKILLS
%====================
\section*{Skills}
\textbf{Backend:} Node.js, Express.js, TypeScript, JavaScript (ES6+), PHP, Laravel, Django, REST APIs, WebRTC, AWS Chime\\
\textbf{Frontend:} React.js, Next.js, HTML5, CSS3, SASS, JavaScript, jQuery\\
\textbf{Databases:} MySQL, TypeORM, Prisma ORM\\
\textbf{Deployment/DevOps:} Docker, Kubernetes, Google Cloud Platform (GCP), DigitalOcean, Nginx, Linux Server Admin, Travis CI\\
\textbf{Version Control \& CI/CD:} Git, GitHub, GitHub Actions\\
\textbf{Tools/IDEs:} VS Code, Postman, phpMyAdmin\\
\textbf{Operating Systems:} Ubuntu/Debian Linux, Windows

%====================
% EDUCATION
%====================
\section*{Education}
\textbf{Bachelor of Science in Computer Science and Software Engineering}\\
American International University -- Bangladesh \hfill Sep 2013 -- Jan 2018 \hspace{1em} CGPA: 3.89 / 4.00

\end{document}
