\documentclass[a4paper,10pt]{article}

\usepackage[margin=1.1cm]{geometry} % slightly tighter margin
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{charter}
\usepackage[none]{hyphenat}
\linespread{1.0} % was 1.05

\sloppy
\clubpenalty=10000
\widowpenalty=10000
\brokenpenalty=10000

\pagenumbering{gobble}
\setlength{\parskip}{1pt} % was 3pt
\setlist[itemize]{topsep=1pt,itemsep=0.7pt,parsep=0pt,leftmargin=12pt} % tighter lists
\titlespacing*{\section}{0pt}{4pt}{3pt} % tighter section spacing
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]

\begin{document}

%====================
% HEADER
%====================
{\LARGE \textbf{Protick Roy}}\\[-1pt]
Dhaka, Bangladesh \\
\href{mailto:protickrr@gmail.com}{protickrr@gmail.com} \textbar{} \href{tel:+8801301212424}{+8801301212424} \textbar{} 
\href{https://www.linkedin.com/in/protickroy}{linkedin.com/in/protickroy} \textbar{} 
\href{https://github.com/protickr}{github.com/protickr}

\vspace{3pt}

%====================
% SUMMARY
%====================
\section*{Summary}
Software Engineer with six years of experience building SaaS, EdTech, ERP, and real-time communication platforms. Designs scalable backends, APIs, and cloud solutions; improves performance, hardens workflows, and ensures high availability. Focused on clean, maintainable code and reliable delivery.

\vspace{3pt}

%====================
% EXPERIENCE
%====================
\section*{Experience}

\textbf{Software Engineer} \hfill Aug 2023 -- Present\\[-2pt]
\textit{Ngaze Inc. \textbar{} Dhaka, Bangladesh}\\[-4pt]
\begin{itemize}
  \item Translated stakeholder requirements into data models and production-ready features, achieving near-perfect alignment with customer needs and reducing rework.
  \item Engineered stateless, type-safe REST APIs with consistent validation/serialization and data integrity guarantees, cutting integration bugs reported by frontend teams by \textasciitilde{}30\% and speeding feature integration.
  \item Built a content versioning system to publish, update, and archive without impacting live content, reducing publishing errors by \textasciitilde{}25\% and eliminating rollback downtime.
  \item Integrated payment gateways in a modular framework, enabling new gateways to be added in under a day and reducing integration effort by \textasciitilde{}70\%.
  \item Implemented BullMQ job queues for reporting/analytics, improving dashboard load times and boosting responsiveness for users.
  \item Ensured reliability of CI/CD pipelines and Kubernetes workloads on GCP; troubleshot failures, added monitoring, and deployed new services for staging and production.
\end{itemize}
\emph{TypeScript, Fastify, React, Next.js, SCSS, BullMQ, Stripe, Redis, Docker, Kubernetes, GCP, GitHub Actions}

\vspace{1pt}

\textbf{Software Engineer (Contract)} \hfill Oct 2020 -- Jul 2023\\[-2pt]
\textit{Omnisoft Lab \textbar{} Dhaka, Bangladesh}\\[-4pt]
\begin{itemize}
  \item Led project work across backend APIs, frontend integrations, cloud deployments, and monitoring; set up repos, pipelines, and release processes.
  \item \textbf{Dollabills} (\href{https://dollabills.club}{dollabills.club}): Built real-time messaging, voice/video calling, and streaming; optimized queries for scale.
  \item \textbf{CPRExchange} (\href{https://cprexchange.com}{cprexchange.com}): Integrated PayPal/Stripe, implemented OTP auth, and managed staging deployments.
\item \textbf{Inventory \& HR Management System} (Shamima Rashid Enterprise, offline): Designed role-based authorization, HR and inventory modules; introduced FIFO stock clearance; deployed and maintained on DigitalOcean.
\end{itemize}
\emph{TypeScript (Express.js, Next.js, TypeORM), PHP (Laravel), MySQL, AWS (Chime, Kinesis, S3, EC2, Route53), DigitalOcean, PM2, Nginx, WebRTC, WebSocket}

\vspace{1pt}

\textbf{Junior Software Engineer} \hfill Sep 2019 -- Apr 2020\\[-2pt]
\textit{Divine IT Limited \textbar{} Dhaka, Bangladesh}\\[-4pt]
\begin{itemize}
  \item Built ERP features and integrated the in-house Central Authentication System; resolved client-specific ERP bugs.
  \item Developed an attendance device monitoring system to ingest/normalize multi-model device data, sync with ERP, and improve HR reporting.
\end{itemize}
\emph{Python (Django, SQLAlchemy), HTML, JavaScript, jQuery, CSS, Git/GitLab, MySQL, SQLite, Agile/Scrum, Linux Mint}

%====================
% PROJECTS
%====================
\section*{Projects}
\begin{itemize}
  \item \textbf{Video Surveillance \& Security System} (\href{https://github.com/protickr/video_surveillance_and_security_system}{github.com/protickr/video\_surveillance\_and\_security\_system}): IoT Computer Vision system that detects motion in real time and emails snapshot alerts (Raspberry Pi + cloud).
  \item \textbf{The Wild Oasis} (\href{https://oasisprotick.vercel.app/login}{oasisprotick.vercel.app/login}): Hotel management app with secure auth, booking flows, and admin dashboard (React/Redux, Vercel).
\end{itemize}

%====================
% SKILLS
%====================
\section*{Technical Skills}
\begin{itemize}[leftmargin=12pt]
  \item \textbf{Languages:} JavaScript, TypeScript, Python, PHP, SQL
  \item \textbf{Frameworks \& Libraries:} Express.js, Fastify, Django, Laravel, Next.js, React, Tailwind
  \item \textbf{Databases/ORM:} MySQL, MongoDB, Redis, Prisma, TypeORM, SQLAlchemy
  \item \textbf{Cloud/DevOps:} Docker, Kubernetes, Nginx, Apache, GCP, AWS, DigitalOcean, CI/CD
  \item \textbf{Other:} HTML5, CSS3/SCSS, Git/GitHub/GitLab, Postman, Linux, macOS
  \item \textbf{Preferred Stack:} TypeScript | Fastify (REST/JSON) | Next.js | MySQL + Prisma | Docker \& K8s | GCP
\end{itemize}

%====================
% EDUCATION
%====================
\section*{Education}
\textbf{Bachelor of Science in Computer Science and Software Engineering}\\
American International University--Bangladesh \hfill Sep 2013 -- Jan 2018 \hspace{1em} CGPA: 3.89 / 4.00

\end{document}
