\documentclass[a4paper,10pt]{article}

\usepackage[margin=1.2cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{charter} % Use Charter font
\usepackage[none]{hyphenat} % Disable word breaks
\linespread{1.05} % Slightly increase line spacing
\sloppy % Prevent overfull lines

% Keep sections from breaking badly across pages
\clubpenalty=10000
\widowpenalty=10000
\brokenpenalty=10000

% Formatting tweaks
\pagenumbering{gobble} % remove page numbers
\setlength{\parskip}{3pt}
\setlist[itemize]{topsep=2pt,itemsep=2pt,parsep=0pt,leftmargin=12pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]

\begin{document}

%====================
% HEADER
%====================
{\LARGE \textbf{Protick Roy}}\\[-1pt]
Dhaka, Bangladesh \\
\href{mailto:protickrr@gmail.com}{protickrr@gmail.com} \textbar{} +8801301212424 \textbar{} 
\href{https://www.linkedin.com/in/protickroy}{linkedin.com/in/protickroy} \textbar{} 
\href{https://github.com/protickr}{github.com/protickr}

\vspace{6pt}

%====================
% SUMMARY
%====================
\section*{Summary}
Software Engineer with over 5 years of experience building SaaS, EdTech, ERP, and real-time communication platforms. 
Skilled in designing scalable backend systems, APIs, and cloud solutions, with a track record of improving performance, 
implementing secure workflows, and ensuring high availability. 
Passionate about writing clean, maintainable code and delivering reliable software that makes a meaningful impact.

\vspace{6pt}

%====================
% SKILLS
%====================
\section*{Technical Skills}
\begin{itemize}[leftmargin=12pt]
  \item \textbf{Languages:} TypeScript, JavaScript, Python, PHP, SQL
  \item \textbf{Frontend:} HTML5, CSS3, SCSS
  \item \textbf{Frameworks \& Libraries:} Express.js, Fastify, Django, Laravel, Next.js, React, Tailwind
  \item \textbf{Databases \& ORM:} MySQL, MongoDB, Redis, Prisma, TypeORM, SQLAlchemy, Eloquent
  \item \textbf{Tools \& Practices:} Git, GitHub/GitLab, Postman, Agile/Scrum
  \item \textbf{Cloud \& DevOps:} Docker, Kubernetes, Nginx, Apache, GCP, AWS, DigitalOcean, CI/CD
  \item \textbf{Environments:} Linux, macOS
  \item \textbf{Preferred Stack:} TypeScript, Fastify (REST/JSON), MySQL, Prisma, Next.js, SCSS, Docker, K8s, GCP
\end{itemize}

\vspace{6pt}

%====================
% EXPERIENCE
%====================
\section*{Experience}

\textbf{Software Engineer} \hfill Aug 2023 – Present\\[-2pt]
\textit{Ngaze Inc. \textbar{} Dhaka, Bangladesh}\\[-4pt]
\begin{itemize}
  \item Translated stakeholder requirements into data models and production-ready features, improving alignment with customer needs.
  \item Engineered stateless, type-safe REST APIs with consistent validation/serialization and data integrity guarantees, adhering to design principles and providing an intuitive, easy-to-integrate consumer interface.
  \item Built a content versioning system that enabled EdTech admins to publish, update, and archive content without affecting live versions, reducing publishing errors and streamlining content management.
  \item Integrated payment gateways within a modular framework, allowing easy addition of future gateways.
  \item Restructured the backend into a modular, standardized architecture, improving maintainability, scalability, and onboarding for new developers.
  \item Implemented BullMQ job queues for long-running processes (e.g., reporting, analytics), reducing dashboard load times and improving responsiveness.
  \item Ensured reliability of CI/CD pipelines and Kubernetes workloads on GCP by troubleshooting failures and monitoring logs for live issues, and configured/deployed new services for staging and production.
  \item Partnered with frontend developers to refine API usability and ensure smooth adoption during integration.
  \item Collaborated with senior engineers on architecture decisions, securing approvals for major feature implementations.
\end{itemize}
\emph{TypeScript, Fastify, React, Next.js, SCSS, BullMQ, Stripe, Redis, Docker, Kubernetes, GCP, GitHub Actions}

\vspace{1pt}

\textbf{Software Engineer (Contract)} \hfill Oct 2020 – Aug 2023\\[-2pt]
\textit{Omnisoft Lab \textbar{} Dhaka, Bangladesh}\\[-4pt]
\begin{itemize}
  \item Collaborated with the core development team on project-based contracts, often acting as a lead by unblocking teammates, reviewing designs, and guiding implementation across system architecture, backend APIs, frontend integrations, cloud deployments, and monitoring.
  \item Established project structures, version control workflows, development/testing pipelines, and deployment processes to ensure consistent and reliable delivery.
  \item \textbf{Dollabills} (\href{https://dollabills.club}{dollabills.club}): Social platform with real-time chat and video conferencing; implemented real-time messaging, voice/video calling, and streaming features, while optimizing queries and ensuring scalable performance.  
  \item \textbf{Inventory \& HR Management System} (Shamima Rashid Enterprise, offline): Designed role-based authorization, HR, and inventory modules; introduced FIFO stock clearance methodology after client ambiguity, enabling accurate reporting and stock flow. Deployed and maintained on DigitalOcean.
  \item \textbf{CPRExchange} (\href{https://cprexchange.com}{cprexchange.com}): Recommerce marketplace with product listings and secure payments; integrated PayPal and Stripe payments, implemented OTP service for authentication, and managed staging deployment.
  \end{itemize}
\emph{TypeScript (Express.js, Next.js, TypeORM), PHP (Laravel), MySQL, AWS (Chime, Kinesis, S3, EC2, Route53), DigitalOcean, PM2, Nginx, WebRTC, WebSocket}


\vspace{1pt}


\textbf{Junior Software Engineer} \hfill Sep 2019 – Apr 2020\\[-2pt]
\textit{Divine IT Limited \textbar{} Dhaka, Bangladesh}\\[-4pt]
\begin{itemize}
  \item Developed ERP modules, starting with CRUD features and later advancing to core engineering tasks, integrating the internal central authentication system, and resolving client-specific ERP bugs.
  \item Built an attendance device monitoring system to ingest and normalize multi-model device data, sync with ERP, and improve HR reporting accuracy.
  \item Collaborated directly with business analysts, product managers, IT/deployment teams, and executives; wrote deployment documentation to support cloud rollouts.
\end{itemize}
\emph{Python (Django, SQLAlchemy), HTML, JavaScript, jQuery, CSS, Git/GitLab, MySQL, SQLite, Agile/Scrum, Linux Mint}

\vspace{1pt}

\textbf{Junior Software Engineer} \hfill Oct 2018 – Jul 2019\\[-2pt]
\textit{BFIN IT Limited \textbar{} Dhaka, Bangladesh}\\[-4pt]
\begin{itemize}
  \item Developed and maintained ERP modules using PHP, JavaScript, jQuery, and Bootstrap, ensuring stability and usability for business operations.
  \item Integrated payment gateways and third-party APIs to enable secure online transactions and expand ERP functionality.
  \item Collaborated with senior engineers on debugging, feature rollouts, and client requests, gaining experience in full-stack workflows and production deployments.
\end{itemize}
\emph{PHP, JavaScript, jQuery, Bootstrap, Payment Gateway Integration}

%====================
% PROJECTS
%====================
\section*{Projects}
\begin{itemize}
  \item \textbf{Video Surveillance \& Security System} (\href{https://github.com/protickr/video_surveillance_and_security_system}{github.com/protickr/video\_surveillance\_and\_security\_system}): IoT system using computer vision to detect motion in real time and send email alerts; included Raspberry Pi setup and cloud deployment.\\
  \emph{Python, OpenCV, Raspberry Pi, Shell, PHP, JavaScript}
  \vspace{1pt}
  \item \textbf{The Wild Oasis} (\href{https://oasisprotick.vercel.app/login}{oasisprotick.vercel.app/login}): Hotel management app with secure auth, booking flows, and admin dashboard; state managed with Redux and deployed on Vercel.\\
  \emph{React, Redux, Supabase, styled-components, Vite, Vercel}
\end{itemize}

%====================
% EDUCATION
%====================
\section*{Education}
\textbf{Bachelor of Science in Computer Science and Software Engineering}\\
American International University — Bangladesh \hfill Sep 2013 – Jan 2018 \hspace{1em} CGPA: 3.89 / 4.00

\end{document}
